The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-08-30 design.tex
rought script

% !TEX root = Eco-Model.tex
\section{Design of the ecosystem} % (fold)
\label{sec:design_of_the_ecosystem}
\subsection{Preliminaries} % (fold)
\label{sub:preliminaries}
The manufacturing ecosystem we proposed in this paper consists of the structure of cloud manufacturing, the operation mode and the controlling rules. Before the detailed interpretation for these parts, we describe some basic settings as follows.

\begin{figure}[htbp]
    \centering
    \resizebox{0.9\textwidth}{!}{\input{figures/origin_mode}}
    \caption{Origin mode}
    \label{fig:originmode}
\end{figure}

@@

\subsection{Individual decisions and ecosystem mode options} % (fold)
\label{sub:interactions_and_decisions}

>>>>

% !TEX root = Eco-Model.tex
\section{Design of the ecosystem} % (fold)
\label{sec:design_of_the_ecosystem}
\subsection{Preliminaries} % (fold)
\label{sub:preliminaries}
Inspired by the cloud manufacturing architecture proposed by research predecessor,

With the cloud manufacturing platform operating, demander arrives, signs up and publishes orders, the structure of the order is depicted by a so-called activity-on-node(AON) network where the nodes represent the tasks and the arcs the precedence relations. Match module in platform informs the task messages to every matched resource provider. After the select decision makes by the demander, the selected resources and services prepare to the performance of the task.
Providers find frequent task after a bunch of successful accomplishment via resource reviews, then another type of job, service-call generated by them to gather certain type and amount of resources registered in the platform to create service in order to perform the certain task more efficient than before. Most of resource related decision making are well controlled by platform with the review module.

Most recent studies like Wu et al.\cite{Wu2013} described the roles in Cloud Manufacturing as a tri-group model with:\begin{inparaenum}[1)]
\item Users/Customers,
\item Application providers and
\item Physical resource providers.
\end{inparaenum}
The manufacturing ecosystem we proposed in this paper consists of the structure of cloud manufacturing, the operation mode and the controlling rules. Before the detailed interpretation for these parts, we describe some basic settings as follows.

\begin{figure}[htbp]
    \centering
    \resizebox{0.9\textwidth}{!}{\input{figures/origin_mode}}
    \caption{Original mode}
    \label{fig:originmode}
\end{figure}

@@

\subsection{Individual decisions and extension modes} % (fold)
\label{sub:interactions_and_decisions}

### 2016-08-30 figures/origin_mode.tex
rought script

% !TEX root = flow_head.tex
\begin{tikzpicture}[node distance=5mm and 5mm,
square/.style={
% The shape:
rectangle,
draw=black,
minimum size=2.9em,
text width=5em,
text centered
},
circle/.style={
rectangle,minimum size=1em,rounded corners=0.5em,
draw=black
}
]
\matrix[row sep=0.5em,column sep=2em] {
% First row:
\node (order) {Demander};& \node (task) [square]{Publish Tasks}; &  & \node (select) [square]{Selection}; & & &  \node (finish) {Product}; \\
\node (start) {}; & & & & & & \node (stop) {}; \\
\node (provider) {Provider};  & \node (resource) [square]{Provide Resources}; & \node (response) [square] {Response Task}; & \node (candidate) [square]{Add to Candidates}; & \node (match) [square]{Assign Task}; & \node (coord) [square] {Cooperate \& Process};&\\
};
\draw[dotted,thick] (start.west) -- (stop.east);
\path (task) edge[->,dashed] (response) (response) edge[->] (candidate) (candidate) edge[->] (select) (select) edge[->] (match) (match) edge[->] (coord) (coord) edge[->] (finish);
% \path (order) edge[->] (task) (task) edge[->] (match) (match) edge[->] (coord) (coord) edge[->] (process) (process) edge[->] (finish) (provider) edge[->] (resource) (resource) edge[->] (match);
\end{tikzpicture}

>>>>

% !TEX root = flow_head.tex
\begin{tikzpicture}[node distance=5mm and 5mm,
square/.style={
% The shape:
rectangle,
draw=black,
minimum size=2.9em,
text width=5em,
text centered
},
circle/.style={
rectangle,minimum size=1em,rounded corners=0.5em,
draw=black
}
]
\matrix[row sep=0.5em,column sep=2em] {
% First row:
\node (order) {Demander};& \node (task) [square]{Publish Tasks}; &  & \node (select) [square]{Selection}; & & &  \node (finish) {Product}; \\
\node (start1) {}; & & & & & & \node (stop1) {}; \\
\node (plt) {Platform} ; & &  \node (tb) [square] {Task Hub} ; & \node (candidate) [square] {Resource Candidates} ; & \node (coop) [square] {Cooperate Resources}; & \node (combine) [square] {Task Assembly};\\
\node (start2) {}; & & & & & & \node (stop2) {}; & \\
\node (provider) {Provider};  & \node (resource) [square]{Provide Resources}; & \node (response) [square] {Response Task}; & \node (add) [square]{Add to Candidates}; & \node (match) [square]{Assign Task}; & \node (process) [square] {Process Task Part};  &\\
};
\draw[dotted,thick] (start1.west) -- (stop1.east) (start2.west) -- (stop2.east);
\path[->,dashed] (task.east) edge (tb.north) (tb) edge (response) (add) edge (candidate) (candidate) edge (select) (match) edge (coop) (coop.east) edge (process.west);
\path[->] (response) edge (add) (select.east) edge (match.west) (process) edge (combine) (combine.north) edge (finish.west);
% \path (order) edge[->] (task) (task) edge[->] (match) (match) edge[->] (coord) (coord) edge[->] (process) (process) edge[->] (finish) (provider) edge[->] (resource) (resource) edge[->] (match);
\end{tikzpicture}

### 2016-08-30 head.tex
change without design.tex
rought script

\author[label1]{Shengkai Chen}
% \address[label1]{ZJU}
% \address[label1]{Address One}
\address[label1]{Zhejiang University, Institute of manufacturing engineering and automation, Hangzhou City, Zhejiang Province, China}

@@

\begin{abstract}
In Cloud Manufacturing, users engage in manufacturing business through the well-designed platform framework, where provider publish manufacturing resource as service for demander to search and purchase it as product. This business model allows centralized management of distributed massive manufacturing resources, and could potentially reduce the idle rate of those resources.

However, in the manufacturing ecosystem constructed with the platform, provider, demander and other components came along with, the heterogeneity of resource's attribute like type, quality, price, processing velocity, leads tough taxonomy of these resources, and the chaotic operating model, makes it hard to meet demander's need.
Thus the way that each provider transforms his/her resource into product with servitization and optimization, constitutes a central issue in such manufacturing ecosystem, all these servitization and optimization activities brings the transition to the individual in the ecosystem. As a consequence, the emergence of manufacturing service pattern will be accompanied by these transitions.

In this paper, the author proposed an operation model for users to support their transitions by means of expanding or shrinking their scope of manufacturing service in the manufacturing ecosystem, and the author also proposed an adjustment approach, which depends on the ranking value of user, for the system to restrict the expanding or shrinking procedure and to control the number of users. Gradually this adjustment will guide the evolution of the ecosystem, meanwhile, good service pattern will be discovered by the user to survival.

With the help of Repast Simphony, the author designed an agent-based model to simulate the evolution process.
As the simulation output, manufacturing resource's quality is improving and its diversity is increasing as the evolution process goes by. The emergence pattern of service and resource optimization implies the effectiveness and validity of the proposed operation model and adjustment approach, user's rank-based transitions does improve the utilization of manufacturing resource.

\end{abstract}

\begin{keyword}
Cloud manufacturing ecosystem \sep
Resource servitization and optimization\sep
Service pattern recognition\sep
Manufacturing evolution\sep
Agent-based simulation

>>>>

\author[label1]{Shengkai Chen}
\author[label1]{Shuiliang Fang}
% \address[label1]{ZJU}
% \address[label1]{Address One}
\address[label1]{Zhejiang University, Institute of manufacturing engineering and automation, Hangzhou City, Zhejiang Province, China}

@@

\begin{abstract}
In Cloud Manufacturing, individuals engage in manufacturing business through the well-designed platform framework, where provider provide manufacturing resource for demander to search and purchase it as product. This business model allows centralized management of distributed massive manufacturing resources, and could potentially reduce the idle rate of those resources.
However, in the manufacturing ecosystem constructed, the heterogeneity of resource's attribute like type, quality, price, processing velocity, leads tough taxonomy of these resources, and the chaotic operating mode, makes it hard to meet demander's need. Meantime, in order to enhance the cash flow rate, provider make decisions to enhance the use rate of their own resources.
The relationship among participants in this ecosystem become more complicated than that in normal manufacturing system, since the integrated advanced technologies within cloud environment makes it possible to let one individual make decisions depend on the surroundings and other's decisions. Hence, in this paper, we designed an original operation mode with 3 extension options for the cloud manufacturing ecosystem to support some decision makings for individuals and the platform operator.
With the help of Repast Simphony, we designed an agent-based model and experiment to simulate these operation modes with any combinations to validate the effectiveness of them. As the experiment result, incubation mode can help reduce the waiting of job and accelerate the process velocity of resources, outsourcing mode reduce the job queue length but not as much as incubation mode and requires more resources, metabolism mode require lower resources than the other modes and will slow resource process velocity a little. The combination of incubation and metabolism mode is ideal for platform operators to maintain the manufacturing ecosystem.
\end{abstract}

\begin{keyword}
Cloud manufacturing ecosystem \sep
Resource servitization and optimization\sep
Operation mode\sep
Manufacturing evolution\sep
Agent-based simulation

### 2016-08-30 intro.tex
rought script

% !Mode:: "TeX:UTF-8"
% !TEX root = Eco-Model.tex
\section{test}

>>>>

% !TEX root = Eco-Model.tex
\section{Introduction}
With the emergence of cloud manufacturing, the relationship among participants in this manufacturing system become more complicated than that in normal manufacturing system, since the integrated advanced technologies within cloud environment makes it possible to let one individual make decisions depend on the surroundings and other's decisions. Demander prefer high quality performance on their needs while provider prefer high use rate of their resource, even the cloud platform operator prefer lower amount of registered resource when dealing with almost arriving needs for the easier maintenance. These preferences stimulate the emergence of good service pattern that will lead to the evolution of manufacturing pattern in the cloud circumstance like an ecosystem. Hence, hence it's important to identify good operation mode that help the evolution.

In this paper, we designed an original operation mode for the cloud manufacturing ecosystem, then we proposed 3 extension modes named metabolism mode, incubation mode and outsourcing mode, that can be extended on the original mode with any combinations. Finally, we deigned an experiment to validate these synthetic operation modes in agent-based simulation method.

### 2016-08-30 review.tex
rought script

Review on 1. Cloud manufacturing mode (any) study 
2. res ser combination and decision making
3. rank and review ecosystem (system changing)
4. manufacturing system simulation

In cloud manufacturing context, centralized management for manufacturing services that encapsulated with distributed manufacturing resources can be realized by an appropriate business model\cite{Xu2012}

Currently, the literature review indicates that modular approaches and multi-layer architectures are the most common way to build the cloud manufacturing platform or system framework (\cite{Tao2012}\cite{Valilai2013}

Most recent studies like Wu et al.\cite{Wu2013} described the roles in Cloud Manufacturing as a tri-group model with:\begin{inparaenum}[1)]
\item Users/Customers,
\item Application providers and
\item Physical resource providers.
\end{inparaenum}

\subsection{Study background} % (fold)
\label{sub:background}

here we goes the terminology that will use in the following subsections within this section. all the related basic terms will in italics fonts.
\begin{itemize}
	\item order
	\item task correspond to capacity
	\item resource
	\item capacity is the function of a resource. like quantity
	\item service is the bundle of capacities. the proportion of the capacities.
	\item 
\end{itemize}

Combined with the background of the research problem and other scholars' previous study in cloud manufacturing, we proposed an improved framework that suits for cloud manufacturing environment

As defined above, Enterprise User is the special case of the User(short for Generalized User) that purely provides manufacturing services and the Customer User is similarly defined.

Hence, there is only two roles in the Ecosystem worth to be studied: User and Administrator, the proportion of user type could be adjusted as the runtime of the system goes by.

% section literature_review (end)

>>>>

In cloud manufacturing context, centralized management for manufacturing services that encapsulated with distributed manufacturing resources can be realized by an appropriate business model\cite{Xu2012}, modular approaches and multi-layer architectures are the most common way to build the cloud manufacturing platform or system framework\cite{Tao2012,Valilai2013}, Lv use list of views to depict this multi-layer architecture\cite{LvJuly312012-Aug.22012}.

Servitization is the key philosophy in the operating of cloud manufacturing\cite{li2010cloud}, service can be created statically that come along with provider\cite{Tao2012} or can be created dynamically according to task pattern, such method as `Multi-Composition for Each Task'\cite{Liu2013} that combine incompetent service into a whole, also service can be created by AI planning-based automatic composition framework\cite{OhJan.-March2008}.

Simulation approach have been widely use in manufacturing system on operations planning and scheduling, real-time control, operating polities, performance analysis\cite{Smith2003}, and in the operating policies field, scheduling policies can be tested with simulation performance under given machine conditions\cite{Sabuncuoglu2003}, machine
segmentation policies can be simulated in a combined MRP and Kanban production system\cite{Felberbauer9-12Dec.2012}. Mourtzis et al.\cite{Mourtzis2015} explored a series of simulation-based solutions in industrial practice and considered research discuss trends are Internet and cloud based situation.

\subsection{Background} % (fold)
\label{sub:background}

In the next section, we will design the ecosystem from an original operation mode, then we formulize the each of the decision makings and the extension modes. Before the design of the ecosystem, we specify some basic concept as the study background. 
\begin{compactitem}
	\item Provider: the individual in ecosystem who provide resources;
	\item Resource: the basic task process visualized object with renewable capacity unique type;
	\item Task: the basic visualized object need to be processed with certain type and capacity of resources;
	\item Demander: the individual in ecosystem who publish orders that contain bunch of tasks;
	\item Platform: the place where individual interact with others and environment.
\end{compactitem}
% section literature_review (end)
